A Neural, Parallel Theorem Prover*

### 2019-05-15 papers/FroCoS19/paper.tex
small edits

\subsection{Search}
In the calculus (see Section \ref{section:Calculus}) for this prover, there are two branching factors: each goal has a set of possible inferences, and each inference contains a set of possible sub-goals.
To prove a goal, at least one inference must be proved.
To prove an inference, all the inferences' sub-goals must be proved.
A simple optimisation observation is that sub-goals might well be shared between inferences from all over the search space, so search becomes a directed acyclic graph, alternating between goals and inferences (illustrated in Fig.~\ref{fig:search}).

@@

Search is biased by heuristic evaluation.
The neural heuristic function (see Section \ref{section:heuristic}) evaluates each goal and assigns a score corresponding to whether the network believes that the goal is satisfiable or unsatisfiable.
In order to balance exploitation of promising directions and exploration of all parts of the search space, a principled UCT-based search algorithm is used, as in MonteCoP~\cite{MonteCoP}.
At each sub-goal, the prover chooses the inference maximising the expression
\[
	s + c\sqrt{\frac{\ln N}{n}}
\]
where \(s\) is the score associated with the inference, \(c\) is the exploration parameter (theoretically \(\sqrt{2}\)), \(N\) is the number of visits to the current node, and \(n\) is the number of visits to the child.
After an inference is selected, the least-promising sub-goal is selected, and the selection process continues until a leaf node is reached.
The score \(s\) of a leaf node is the score assigned to it by the heuristic function.
An inference's score is the minimum of their sub-goals' scores, and non-leaf sub-goal's score is the maximum of their inference's scores.

>>>>

\subsection{Search}
In the calculus (see Section \ref{section:Calculus}) for this prover, there are two branching factors: each goal has a set of possible inferences, and each inference contains a set of possible sub-goals.
To prove a goal, at least one inference must be proved.
To prove an inference, all the inferences' sub-goals must be proved (e.g. shown to be unsatisfiable).
A simple optimisation is that sub-goals may be shared between inferences, so search becomes a directed acyclic graph, alternating between goals and inferences (illustrated in Fig.~\ref{fig:search}).

@@

Search is biased by heuristic evaluation.
The neural heuristic function (see Section \ref{section:heuristic}) evaluates each goal and assigns a score corresponding to whether the network believes that the goal is satisfiable or unsatisfiable.
In order to balance exploitation of promising directions and exploration of all parts of the search space, a principled UCT-based search algorithm is used, as in MonteCoP~\cite{MonteCoP}.
At each sub-goal, the prover chooses the inference maximising the expression
\[
	s + c\sqrt{\frac{\ln N}{n}}
\]
where \(s\) is the score associated with the inference, \(c\) is the exploration parameter (theoretically \(\sqrt{2}\)), \(N\) is the number of visits to the current node, and \(n\) is the number of visits to the child. An inference's score is the minimum of their sub-goals' scores, and non-leaf sub-goal's score is the maximum of their inference's scores. The score \(s\) of a goal node is the score assigned to it by the heuristic function. After an inference is selected, the least-promising sub-goal is selected, and the selection process continues until a leaf node is reached.
